Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-06-23 supplements/supplements.Rmd
start working on modeling section

>>>>

## Model comparison

```{r magnet_modelcomparison}
magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```
